---
title: "gtsummary in quarto"
author: Sophia 
format: 
  html: 
    theme: quartz
execute: 
  echo: false
---

*text before code chunk* I'm so hungry right now.

```{r}
#| message: false
library(tidyverse)
library(gtsummary)
nlsy_cols <- c("glasses", "eyesight", "sleep_wkdy", "sleep_wknd", 
               "id", "nsibs", "samp", "race_eth", "sex", "region", 
               "income", "res_1980", "res_2002", "age_bir")
nlsy <- read_csv(here::here("data", "raw", "nlsy.csv"), 
                 na = c("-1", "-2", "-3", "-4", "-5", "-998"),
                 skip = 1, col_names = nlsy_cols) |> 
  mutate(region_cat = factor(region, labels = c("Northeast", "North Central", "South", "West")),
         sex_cat = factor(sex, labels = c("Male", "Female")),
         race_eth_cat = factor(race_eth, labels = c("Hispanic", "Black", "Non-Black, Non-Hispanic")),
         eyesight_cat = factor(eyesight, labels = c("Excellent", "Very good", "Good", "Fair", "Poor")),
         glasses_cat = factor(glasses, labels = c("No", "Yes"))) 
```

# Customization of `tbl_summary()`

```{r}
#| label: tbl-one
#| tbl-cap: "Basic Characteristics-ver 0."
tbl_summary(
  nlsy,
  by = sex_cat,
  include = c(sex_cat, race_eth_cat, region_cat,
              eyesight_cat, glasses, age_bir))
```

```{r}
#| label: tbl-two
#| tbl-cap: "Basic Characteristics"
tbl_summary(
  nlsy,
  by = sex_cat,
  include = c(sex_cat, race_eth_cat, region_cat,
              eyesight_cat, glasses, age_bir),
  label = list(
    race_eth_cat ~ "Race/ethnicity",
    region_cat ~ "Region",
    eyesight_cat ~ "Eyesight",
    glasses ~ "Wears glasses",
    age_bir ~ "Age at first birth"
  ),
  missing_text = "Missing")
```

@tbl-one and @tbl-two shows the descriptive stastistics.

```{r}
#| label: tbl-three
#| tbl-cap: "Doesn't Matter"
tbl_summary(
  nlsy,
  by = sex_cat,
  include = c(sex_cat, race_eth_cat, region_cat,
              eyesight_cat, glasses, age_bir))
```

```{r}
#for this code to work you'll need to run the previous codes !the first chunk! first.
mean_wkdy <- mean(nlsy$sleep_wkdy, na.rm = TRUE)
median_wkdy <- median(nlsy$sleep_wkdy, na.rm = TRUE)
```
The mean of sleeping time on weekdays is `r round(mean_wkdy, 2)`.
The median of sleeping time on weekdays is `r round(median_wkdy, 2)`.
```{r}
#| label: tbl-four
#| tbl-cap: "Exercise 2.3.2"

table4 <-tbl_summary(
  nlsy,
  by = sex_cat,
  include = c(sex_cat, race_eth_cat, region_cat,
              eyesight_cat, glasses, age_bir, sleep_wkdy)) |>
	add_overall(last = TRUE)
table4
south_overall <- inline_text(table4, variable = "region_cat", level = "South", column = "stat_0")
med_f_wkdy <- inline_text(table4, variable = "sleep_wkdy", column = "stat_2")
```
There are `r south_overall` cats from the south region.
The median of sleeping time on weekdays for female cats is `r med_f_wkdy`.
